$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2014-03-17 JournalToSubmit2013/modelingWithPISODM.tex
Version for starting the week

As shown in Table \ref{fig:ServiceComposition-Pews-Rules}, for an event of type Pre the corresponding transformed rule is a {\sf Precondition}; for an event of type Post the corresponding transformed rule is a {\sf Post- condition}; finally, for an event of type TimeRestriction the corresponding transformed rule is a {\sf Time}. The condition expression of a rule in a $\pi$-service composition ({\sf Rule:condition}) is transformed into a  {\sf Condition:expression} where the attributes of the expression are transformed into  entities {\sf Attribute}.

>>>>

%As shown in Table \ref{fig:ServiceComposition-Pews-Rules}, 
For an event of type Pre the corresponding transformed rule is a {\sf Precondition}; for an event of type Post the corresponding transformed rule is a {\sf Post- condition}; finally, for an event of type TimeRestriction the corresponding transformed rule is a {\sf Time}. The condition expression of a rule in a $\pi$-service composition ({\sf Rule:condition}) is transformed into a  {\sf Condition:expression} where the attributes of the expression are transformed into  entities {\sf Attribute}.
